Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-04 paper/main.tex
added comment about the model

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{stream_on_sky_Pal5_monte-carlo-009_pouliasis2017pii-GCNBody.png}
    \caption{An instsance of the Palomar 5 stream created modeling the cluster as a Plummer sphere within an axis-symmetric galactic potential plus 164 other galactic globular clusters. The top plot is a scatter plot of star-particles that escaped the cluster due to tidal forces, the bottom plot shows the marginalized 1D density profile in longitude. Two large gaps are present and are due to the passage of two globular clusters. $N_p$ indicates the number of particles in a bin while $N$ is the total number of particles which is 100,000.}
    \label{fig:stream_on_sky}
    \end{figure*}

@@

>>>>

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{paper/stream_on_sky_Pal5_monte-carlo-009_pouliasis2017pii-GCNBody_pouliasis2017pii.png}
    \caption{Simulated Palomar 5 sstream created by modeling the host cluster as a Plummer sphere disrupting within an axis-symmetric galactic potential plus the gravitational effect of 164 other galactic globular clusters. The top panel shows the distribution of star-particles that escaped the cluster due to tidal forces. The bottom panel shows the 1D density profile marginalized over longitude. The gray fill shows a reference simulation where the same conditions to produce the stream are used but the effect of other globular clusters are not included. The large central peak in density are of the particles still bound to Palomar~5. $\ell_0,b_0$ are located Palomar~5's cluster's center of mass. Two large gaps are present and are due to the passage of two globular clusters. $N_p$ indicates the number of particles in a bin while $N$ is the total number of particles which is 100,000.}
    \label{fig:stream_on_sky}
    \end{figure*}

@@

    Regarding the shape of the density distribution, the central peak corresponds to the still-intact globular cluster whose stars have not yet escaped. The density peaks in the stream are of the same order as the cluster itself. This is inconsistent with reality, the cluster should be much more populated than the stream's peak density. Of course, this discrepency a result of our modeling choices. We use the present day mass and radius for Palomar~5 for the whole duration of the simulation. A consequence of this is that the system is modeled as being less dense than it should have been. In turn, our simulations a strong initial mass which adds to the amplitudes of the profile density peaks of Fig.~\ref{fig:stream_on_sky}. This inaccuracy is acceptable for the scope of this work. First is that Palomar~5's tails indeed have more mass than the cluster itself. \citet{2017ApJ...842..120I} reports that there could be three times as much mass in Palomar 5's tails as the cluster itself. Secondly, the exact form of the density distribution is less important than haing a population of particles present that can probe a cluster flyby event.
